---
title: "Code"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install packages
```{r}
library(tidyverse)
library(rvest)
library(httr)
```

## Download the data
```{r}

# The data has already downloaded, we do not need to rerun the code...
# The output is already in data/original data
while(FALSE)
{
data =
  GET("https://data.cityofnewyork.us/resource/5uac-w243.csv",
      query = list("$limit" = 396978 )) %>% 
  content("parsed")

write_csv(data, file = "data/original_data.csv")
}
```

## data cleaning
```{r}
# extract Manhattan data

cut_off <- 
  as.POSIXct("2010-01-01", format = "%Y-%m-%d")

man_data =
  read_csv("") %>% 
  janitor::clean_names() %>% 
  drop_na(cmplnt_fr_dt) %>% 
  filter(boro_nm == "MANHATTAN",
         cmplnt_fr_dt > cut_off) %>% 
  select(cmplnt_num,
         boro_nm, cmplnt_fr_dt:crm_atpt_cptd_cd,
         ky_cd: rpt_dt,
         susp_age_group:susp_sex,
         vic_age_group:lat_lon) %>% 
  filter(latitude > 40.7865 & latitude < 40.848256,
        longitude > -73.9816 & longitude < -73.79268)

```

In this step, the data is clean and tidied by : 1. select the rows recording date later than 2010-01-01. 2. Select the borogh as Manhattan. 3. select the variables we are interseted in. 4. filter the latitude and longitude to limit it around columbia campus (roughly). The latitude range is approximately from 86 street subway station to George Washing Bridge (West 178th street). The longitude range is from Hudson river to Harlem river and Central park. This region covers Columbia University campus (and CUIMC) and the neighborhood area.


