---
title: "EDA"
author: "Haochen Sun"
date: "2022-12-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(patchwork)
library(plotly)

knitr::opts_chunk$set(
  fig.width = 5,
  out.width = "60%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
# Exploratory Analysis

After reading this page, you will have an overall sense about the crimes around Columbia University campus (including CUIMC). 

We pictured the proportion of each level of crimes, and the charactristic of suspects and victims. We also focused on the total crime numbers across the years, showing a pattern of the fluctation of offense number with the months and times, so that we can have an idea about when it will be more dangerous and need more caution. At the same time, we also captured some interesting point of offense number.

## Overview about offenses around CU campus
```{r EDA}
filter_data = read_csv("../data/full_filter_data.csv")

p <- c() # a list to save plots

p[[1]] <- ggplot(aes(x = level, fill = level), data = filter_data) + 
  geom_bar() +
  labs(x = "Crime Level", y = "Number") + guides(fill = "none")

p[[2]] <- ggplot(aes(x = success_fail, fill = success_fail), data = 
                  filter_data)+
    geom_bar()+
  labs(x = "Crime Completed or Not", y = "Number")+ guides(fill = "none")

p[[1]] + p[[2]]
```

The number of misdemeanor crime is the most (62.1%), which includes simple assault, petty theft, drug possession, indecent exposure, etc. While the number of felony is approximately half of misdemeanor (28.7%), which includes homicide offense, rubbery, burglary, sexual offense, drug crime, etc. The least type is violation (10%), including littering, drinking in public, walking unleashed dog, etc. Here exists a selection bias, most of people would not report a violation to the police. This figure does not indicate violation crimes is the least type in reality. At the meanwhile, nearly all (98%) of the crimes are completed -- do not put your faith in luck that someone can help you, try to avoid them as much as you can! 

Next, we focus on the portrait of suspects and victims.

```{r}
p[[3]] <- filter_data %>% 
  filter(susp_age %in% c("<18", "18-24", "25-44", "45-64", "65+",
                         "UNKNOWN")) %>%
  mutate(susp_age = as.factor(susp_age)) %>% 
  count(susp_age, level) %>% 
  plot_ly(x = ~ susp_age, y = ~n, type = "bar", color = ~ level, colors = "viridis") %>% 
  layout(title = "Suspects' Age Group", xaxis = list(title = ""), yaxis = list(title = "Number"))

p[[4]] <- filter_data %>% 
  filter (susp_race != "(null)") %>% 
  mutate(susp_age = as.factor(susp_race)) %>% 
  count(susp_race, level) %>% 
  plot_ly(x = ~ susp_race, y = ~n, type = "bar", color = ~ level, colors = "viridis") %>% 
  layout(title = "Suspects' Race", xaxis = list(title = ""), yaxis = list(title = "Number"))

p[[5]] <- filter_data %>% 
  filter (susp_sex != "(null)")  %>% 
  mutate(susp_sex = as.factor(susp_sex)) %>% 
  count(susp_sex, level) %>% 
  mutate(susp_sex = recode(susp_sex, U = "Unknown", F = "Female", "M" = "Male")) %>% 
  plot_ly(x = ~ susp_sex, y = ~n, type = "bar", color = ~ level, colors = "viridis") %>% 
  layout(title = "Suspects' Sex", xaxis = list(title = ""), yaxis = list(title = "Number"))
```

```{r}
p[[6]] <- filter_data %>% 
  filter(vic_age %in% c("<18", "18-24", "25-44", "45-64", "65+",
                         "UNKNOWN")) %>%
  mutate(vic_age = as.factor(vic_age)) %>% 
  count(vic_age, level) %>% 
  plot_ly(x = ~ vic_age, y = ~n, type = "bar", color = ~ level, colors = "viridis") %>% 
  layout(title = "Victims' Age Group", xaxis = list(title = ""), yaxis = list(title = "Number"))

p[[7]] <- filter_data %>% 
  filter (vic_race != "(null)") %>% 
  mutate(vic_age = as.factor(vic_race)) %>% 
  count(vic_race, level) %>% 
  plot_ly(x = ~ vic_race, y = ~n, type = "bar", color = ~ level, colors = "viridis") %>% 
  layout(title = "Victims' Race", xaxis = list(title = ""), yaxis = list(title = "Number"))

p[[8]] <- filter_data %>% 
  filter (vic_sex %in% c("D", "E", "F", "M"))  %>% 
  mutate(vic_sex = as.factor(vic_sex)) %>% 
  count(vic_sex, level) %>% 
  mutate(vic_sex = recode(vic_sex, F = "Female", "M" = "Male")) %>% 
  plot_ly(x = ~ vic_sex, y = ~n, type = "bar", color = ~ level, colors = "viridis") %>% 
  layout(title = "Victims' Sex", xaxis = list(title = ""), yaxis = list(title = "Number"))

# detailed description of suspect group
filter_data %>% 
  group_by(susp_age, susp_race, susp_sex) %>% 
  summarise(number = n()) %>% 
  arrange(desc(number))

# detailed description of victim group

filter_data %>% 
  group_by(vic_age, vic_race, vic_sex) %>% 
  summarise(number = n()) %>% 
  arrange(desc(number)))
```


