
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 5,
  out.width = "60%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Time pattern

In the EDA part, we see that there exist some pattern in month and time in one day, but is it only random error and fluctuation, or there exist a significant difference?

## Month

We use group_by and summarize function to get the number of cases in each month and year, and then use the number of cases and month_data to make an ANOVA model to test whether there is a significant difference of number of crime cases among each month. 

```{r}
data <- read_csv("../data/full_filter_data.csv")

month_data <- data %>%  
  group_by(year, month) %>% 
  summarise(number = n()) %>% 
  mutate(month = as.factor(month),
         year = as.factor(year))

aov_model <- aov(number ~ month, data = month_data) 

aov_model %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 4 )
```

By the result above, we find that there are very significant difference in the crime numbers between months. Therefore, we utilized Tukey's method for post hoc tests, to see which months are different. 

Firstly, we use Turkey methods to analogize the ANOVA model, select the variables which p-value are smaller than 0.05, and arrange them by adj p_value. Then, we separate the contrast to A and B and add two variables "high" and "low" depending on whether estimate is larger than 0 to decide how A and B to fit high and low. Finally, we make a two panel plot to show the order of the months become "high" and "low" in the process of comparing. 

```{r}
aov_posthoc <- TukeyHSD(aov_model, conf.level = .95) %>% 
  broom::tidy() %>% 
  filter(adj.p.value < 0.05) %>% 
  arrange(adj.p.value)

aov_posthoc %>% 
  head(5) %>% 
  knitr::kable(digits = 4 )

aov_group <- aov_posthoc %>% 
  separate(contrast, sep = "-", into = c("A", "B")) %>% 
  mutate(high = if_else(estimate > 0, true = A, false = B),
         low = if_else(estimate > 0, true = B, false = A)) %>% 
  mutate(high = fct_infreq(high),
         low = fct_infreq(low))

aov_fig1 <- aov_group %>% 
  ggplot(aes(x = high, fill = high)) +
  geom_bar(stat = "count") +
  labs(x = "Month", y = "Count", title = 
         "Months Having More Crimes \n in Multiple Comparisons") + guides(fill = "none")

aov_fig2 <- aov_group %>% 
  ggplot(aes(x = low, fill = low)) +
  geom_bar(stat = "count") +
  labs(x = "Month", y = "Count",title = 
         "Months Having Fewer Crimes \n in Multiple Comparisons") + guides(fill = "none")

aov_fig1 + aov_fig2
```

After pairwise independent multiple tests, we can draw the conclusion. We can roughly divide the months in one year into 3 groups. July, August, October, May, June, September generally have more crimes. February, January, November, December have fewer crimes. While March and April is at medium level, the crime number in this two months are significantly less than those months with excessive crimes, but also significantly more than months that have fewest crimes.

## Time

Next, we repeat the steps, to see whether crime number at different time in a day have significant difference.

```{r}
# Is there differnece between case numbers in every hour? 
hour_data = data %>% 
  group_by(year, month, hour) %>% 
  summarise(number = n()) %>%
  mutate(hour = as.factor(hour),
    hour = fct_inseq(hour)) 

aov_hour <- aov(number ~ hour, data = hour_data)

aov_hour %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 4 )
```
There are also significant difference in the mean number of crimes between different hours in one day.

```{r}
hour_posthoc <- TukeyHSD(aov_hour, conf.level = .95) %>% 
  broom::tidy() %>% 
  filter(adj.p.value < 0.05) %>% 
  arrange(adj.p.value)

hour_group <- hour_posthoc %>% 
  separate(contrast, sep = "-", into = c("A", "B")) %>% 
  mutate(high = if_else(estimate > 0, true = A, false = B),
         low = if_else(estimate > 0, true = B, false = A)) %>% 
  mutate(high = fct_infreq(high),
         low = fct_infreq(low))

aov_fig3 <- hour_group %>% 
  ggplot(aes(x = high, fill = high)) +
  geom_bar(stat = "count") +
  labs(x = "Hour", y = "Count", title = 
         "Hours Having More Crimes \n in Multiple Comparisons") + guides(fill = "none")

aov_fig4 <- hour_group %>% 
  ggplot(aes(x = low, fill = low)) +
  geom_bar(stat = "count") +
  labs(x = "Month", y = "Count",title = 
         "Months Having Fewer Crimes \n in Multiple Comparisons") + guides(fill = "none")

aov_fig3 + aov_fig4
```

The result corresponded with the findings in EDA part. The most dangerous hour is 12:00 - 21:00, all of them are at high ranks in the left figure. Comparatively, 1:00 - 9:00 is the most peaceful time. But it's our consensus that midnights are more hazardous. So we questioned on if more server levels of crime take place more in the midnights. 

```{r}
hour_level = data %>% 
  group_by(year, month, hour, level) %>% 
  filter(level == "FELONY") %>% 
  summarise(number = n()) %>%
  mutate(hour = as.factor(hour),
    hour = fct_inseq(hour)) 

aov_level <- aov(number ~ hour, data = hour_level)

aov_level %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 4 )

level_posthoc <- TukeyHSD(aov_level, conf.level = .95) %>% 
  broom::tidy() %>% 
  filter(adj.p.value < 0.05) %>% 
  arrange(adj.p.value)

level_group <- level_posthoc %>% 
  separate(contrast, sep = "-", into = c("A", "B")) %>% 
  mutate(high = if_else(estimate > 0, true = A, false = B),
         low = if_else(estimate > 0, true = B, false = A)) %>% 
  mutate(high = fct_infreq(high),
         low = fct_infreq(low))

aov_fig5 <- level_group %>% 
  ggplot(aes(x = high, fill = high)) +
  geom_bar(stat = "count") +
  labs(x = "Hour", y = "Count", title = 
         "Hours Having More Felony Crimes \n in Multiple Comparisons") + guides(fill = "none")

aov_fig6 <- level_group %>% 
  ggplot(aes(x = low, fill = low)) +
  geom_bar(stat = "count") +
  labs(x = "Month", y = "Count",title = 
         "Months Having Fewer Felony Crimes \n in Multiple Comparisons") + guides(fill = "none")

aov_fig5 + aov_fig6
```

The conclusion still holds true. Be cautious! What time you think is safe may be dangerous than your thought.

## Build a linear model for prediction

All variables are categorical, except the response variable crime number. After plotting the histogram, we find the crime number is strongly right-skewed. Using boxcox transformation, we take logrithm of number and the data looks much more normally distributed.

```{r}

# find that group by day, every day there are too few cases, not appropriate for prediction, so we choose to ignore the day variable

lm_data <- data %>% 
  filter(vic_age %in% c("<18", "18-24", "25-44", "45-64", "65+")) %>% 
  filter(vic_sex %in% c("M", "F")) %>%
  filter(vic_race != "(null)") %>% 
  mutate_at(c("month", "hour", "vic_age", "vic_race", "vic_sex"), as.factor) %>% 
  group_by(month, hour, vic_age, vic_race, vic_sex) %>% 
  summarise(log_number = log(n())) 

lm_model <- lm(log_number ~ . , data = lm_data)

options(digits = 4)

summary(lm_model, correlation = FALSE) %>% 
  broom::glance() %>% 
  knitr::kable()
  
cv_result =
  crossv_mc(lm_data, 100) %>% 
  mutate(model = map(train, ~lm(log_number ~ ., data =.x))) %>% 
  mutate(rmse = map2_dbl(model, test,
                         ~rmse(model = .x, data = .y)))

sum_number <- summary(lm_data$log_number) %>% 
  broom::tidy()

IQR <- sum_number$q3 - sum_number$q1

cv_result %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse/IQR)) + geom_boxplot() +
  labs(x = "", y = "RMSE/IQR", title = "Distribution of RMSDIQR")
```

We used normalized RMSE as the reference to evaluate the prediction ability of this model. It turnns of to be good.

