---
title: "hypo"
author: "Yuze Yuan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(patchwork)
library(plotly)
knitr::opts_chunk$set(
  fig.width = 5,
  out.width = "60%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Whether there is a significant difference in the number of male and female suspects. We calculate how many male and female suspects in month, year, then plot the disturbution of number of male and female suspects.
```{r}
data <- read_csv("../data/full_filter_data.csv")
gender_data <- data %>%  
  group_by(year, month, susp_sex) %>% 
  summarise(number = n()) %>% 
  mutate(susp_sex = as.factor(susp_sex)) %>%
  filter(susp_sex %in% c("F", "M", "U"))
aov_model_1 <- aov(number ~ susp_sex, data = gender_data)

summary(aov_model_1)

gender_data %>% 
  ggplot(aes(x = susp_sex, y = number, fill = susp_sex)) +
  geom_boxplot() +
  guides(fill = "none")  
```
* This is a significant difference in the number of male and female suspects. Through the boxplot, we could easily see that male is more likely to be suspencts than females if we consider the unknown.

